Paper Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-11 paper-plan/paper-plan.tex
HouseHold Robot paper

>>>>

\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}

For household robot planning, it appears easy, but actually involves
uncertainty. For tidying things up objects might not be there, or sensing
operations might tell things wrong. This paper looks into conditions for
classical planning in a replanning loop in order to solve nondeterministic
partially observable open domains This paper looks into conditions for
classical planning in a replanning loop in order to solve nondeterministic
partially observable open domains.
